Tickle me BERT: Using laughter to probe pre-trained encoders for dialogue act recoginiton

### 2019-12-09 reports/ACL2020 Paper/acl2020-paper.tex
Some rewording

There is abundant room for further progress in determining how other speech-related information, such as prosody and disfluencies, can be incorporated into the DAR model.
\citet{stolckeDialogueActModeling2000} showed that dialogue acts can have specific prosodic manifestations that can be used to improve dialogue act classification.
Furthermore, function of laughter and its position in relation to laughable can be reflected in the acoustic form of laughter \citep{tian2016we,mazzocconi2019phd}.

>>>>

There is abundant room for further progress in determining how other speech-related information, such as prosody and disfluencies, can be incorporated into the DAR model.
\citet{stolckeDialogueActModeling2000} showed that dialogue acts can have specific prosodic manifestations that can be used to improve dialogue act classification.
Furthermore, in relation to laughter, its form (duration, arousal level) can be informative about its function and position w.r.t. to laughable \citep{tian2016we,mazzocconi2019phd}.
